Project Goal:
Build a glucose prediction model that uses the fewest meaningful predictors to accurately predict glucose levels keeping prediction error low
Optimization: accuracy versus sparsity (fewest predictors)


Insulin Codes: 
33 = Regular insulin dose                               [short-acting insulin (works soon after injection, often around meals)]
34 = NPH insulin dose                                   [intermediate-acting insulin (lasts longer than regular, and is used for background insulin plan)]
35 = UltraLente insulin dose                            [Long-acting insulin (Different role than regular insulin, as its not for immediate spikes)]
48 = Unspecified blood glucose measurement              [Glucose was measured, but not tied to meal context]
57 = Unspecified blood glucose measurement              [^]
58 = Pre-breakfast blood glucose measurement
59 = Post-breakfast blood glucose measurement
60 = Pre-lunch blood glucose measurement
61 = Post-lunch blood glucose measurement
62 = Pre-supper blood glucose measurement
63 = Post-supper blood glucose measurement
64 = Pre-snack blood glucose measurement
65 = Hypoglycemic symptoms                              [symptoms of low blood sugar]
66 = Typical meal ingestion
67 = More-than-usual meal ingestion
68 = Less-than-usual meal ingestion
69 = Typical exercise activity
70 = More-than-usual exercise activity
71 = Less-than-usual exercise activity
72 = Unspecified special event

___________________________________________________________________
We predict a patients pre-meal glucose level using prior insulin, meal, exercise, and previous glucose levels, while selecting a spare set of predictors

# Variables And Definitions:
y_i: glucose value for observation i
x_i: feature vector for observation i

beta: model coefficients
z_j: binary variable indicating whether feature j is selected
c_j: cost or weight for selecting feature j

n: number of training observations
p: number of candidate features
tau: maximum acceptable prediction error
M: sufficiently large constant linking beta_j and z_j

You can say:
y_i comes only from pre-meal glucose rows
x_i may include previous glucose, insulin doses, meal indicators, exercise indicators, Day, MinuteOfDay, and lag features
___________________________________________________________________

# Ideal Optimization Model:
The exact sparse feature-selection problem is:

minimize over beta, z:
sum from j=1 to p of c_j z_j

subject to
(1/n) ||y - X beta||_2^2 <= tau
-M z_j <= beta_j <= M z_j,   for j = 1, ..., p
z_j in {0,1},   for j = 1, ..., p

Meaning
The objective minimizes the number or total cost of selected predictors.
The MSE constraint forces the model to stay accurate enough.
The linking constraint says that if z_j = 0, then beta_j must be zero, so feature j is not used.

___________________________________________________________________
Workflow

1. Load data
    Read all data-01 to data-70 patient files and combine them into one table.

2. Transform raw records
Convert:
    Date to patient-relative Day
    Time to MinuteOfDay
    Code to readable event labels

3. Choose target rows
Keep glucose rows with pre-meal codes:
    58 pre-breakfast
    60 pre-lunch
    62 pre-supper
    64 pre-snack

4. Build predictors for each target row
For each target glucose reading, create features using only earlier events:
    previous glucose
    previous insulin doses
    meal indicators
    exercise indicators
    Day
    MinuteOfDay
    time since last glucose reading
    optional lag summaries like recent average glucose

5. Clean and filter data
Handle:
    malformed dates
    nonnumeric glucose entries like 0Hi, 0Lo
    missing values
    rare or noisy codes if needed

6. Create train/test split
Split by time, not randomly:
    train on earlier records
    validate/test on later records
    This is better because we are predicting future glucose from past events.

# Models / Algorithms
7. Baseline 1: simple mean predictor
    Predict glucose using the average training glucose.
    This gives a weak baseline to beat.

8. Baseline 2: previous glucose predictor
    Predict the next pre-meal glucose using the most recent previous glucose.
    This is often a surprisingly strong baseline.

9. Ridge regression baseline
Fit ridge regression on all engineered features.
Purpose:
    closed-form mathematical baseline
    handles correlated predictors
    good comparison point

10. LASSO regression
Fit LASSO on the same feature set.
Purpose:
    sparse feature selection
    convex optimization model
    easier interpretation

11. Elastic net regression
Fit elastic net on the same feature set.
Purpose:
    combines LASSO sparsity with ridge stability
    usually better when predictors are correlated
    likely your best main model


# Validation / Analysis
17. Compare models
Compare:
    mean baseline
    previous glucose baseline
    ridge
    LASSO
    elastic net

18. Analyze selected predictors
Look at which variables elastic net/LASSO keeps:
    prior glucose
    insulin types
    meal effects
    exercise effects
    time-of-day effects

19. Interpret results
Explain what the selected predictors mean clinically and what the tradeoff is between:
    fewer predictors
    lower prediction error


For more detailed model:
https://www.synapse.org/Synapse:syn38187184/wiki/619491